Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-04 edubots_surveys.Rnw
One hour to edit the table
Which is why, kids, please use knitr to include data into papers.

%TODO - table fits better in landscape? try to fit in page size 
\begin{sidewaystable}[h!tbp]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lllllllllll}
\hline
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Analytics} & Connectivity & Familiarity & Hidden phone & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality \\ \hline
Analytics & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.172^{***}$} & $X^{2}_{(1, N = 205)} = 4.855^{*}$ & ns & ns & $X^{2}_{(1, N = 205)} = 4.144^{*}$ & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.490^{***}$} & $X^{2}_{(1, N = 205)} = 4.314^{*}$ & ns & ns \\
Connectivity & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-} & ns & ns & $X^{2}_{(1, N = 205)} = 5.971^{***}$ & ns & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 16.286^{***}$} & ns & ns & ns \\
Familiarity &  &  & - & ns & ns & ns & ns & ns & ns & ns \\
Hidden phone &  &  &  & - & ns & $X^{2}_{(1, N = 205)} = 5.678^{*}$ & $X^{2}_{(1, N = 205)} = 4.683^{*}$ & ns & $X^{2}_{(1, N = 205)} = 4.515^{*}$ & ns \\
Horizontallity &  &  &  &  & - & ns & ns & ns & ns & $X^{2}_{(1, N = 205)} = 5.453^{*}$ \\
\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  &  &  &  &  & - & $X^{2}_{(1, N = 205)} = 8.163^{**}$ & ns & ns & ns  \\
Synchrony & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  &  &  & \multicolumn{1}{c}{} &  &  & \\ \hline
\end{tabular}}
\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$). Columns and rows with no significant interaction have been suppressed for clarity.}
\label{tab:interactionfeatures}
\end{sidewaystable}

>>>>

%TODO - table fits better in landscape? try to fit in page size 
\begin{table}[h!tbp]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lllllllll}
\hline
 & Connectivity & Familiarity  & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality \\ \hline
Analytics &  $12.172^{***}$ & $4.855^{*}$ & ns & $4.144^{*}$ &  $12.490^{***}$ & $4.314^{*}$ & ns & ns \\
Connectivity & - & ns & $5.971^{***}$ & ns & $16.286^{***}$ & ns & ns & ns \\
Hidden phone &  &  & ns & $5.678^{*}$ & $4.683^{*}$ & ns & $4.515^{*}$ & ns \\
Horizontallity &  &  - & ns & ns & ns & ns & ns & $5.453^{*}$ \\
\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  & &  & - & $8.163^{**}$ & ns & ns & ns  \\
\end{tabular}}
\vspace{0.8em}
\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$). Columns and rows with no significant interaction have been suppressed for clarity. Every cell value represents $X^{2}_{(1, N = 205)}$.}
\label{tab:interactionfeatures}
\end{table}
